\LARGE Tailoring Differentially Private Bayesian Inference to Distance Between Distributions

### 2018-10-09 poster/main.tex
update plots in poster

\begin{block}{Bayesian inference: Beta-Binomial model}
% The first subdivided column within the first main column
% \begin{columns} % Subdivide the first main column
% \begin{column}{.54\textwidth} % The first subdivided column within the first main column
%The prior $\betad(\alpha, \beta)$, with hyperparameters $\alpha,\beta\in\mathbb{R}^{+}$ is conjugate to the likelihood function.
\begin{itemize}
  \item[-] Prior on $\theta: \betad(\alpha, \beta), \alpha,\beta\in\mathbb{R}^{+}$, observed data set $\dataobs= (x_1,\dots x_n)\in\{0,1\}^{n}, n\in\mathbb{N}$.

@@

\begin{block}{Differentially Private Bayesian Inference and Motivation}
Releasing a differentially private posterior $\betad (\tilde\alpha,\tilde\beta)=(\alpha +  \widetilde{\Delta \alpha},\beta + n - \widetilde{\Delta \alpha})$.
\begin{columns} % Subdivide the first main column
\begin{column}{.69\textwidth}
\begin{enumerate}
  \item  Baseline approach samples noise from $\mathsf{Lap}(\Delta \alpha, \frac{1}{\epsilon})$ with mean $\Delta \alpha$ and scale $\frac{1}{\epsilon}$. But noise here is scaled to sensitivity $1$ over $\ell_1$ norm. Motivated by this, we calibrate the noise w.r.t sensitivity of the accuracy metric ($\hellinger$) (v.s. the $\ell_1$ norm in baseline approach).
  \item Global sensitivity of $\hellinger$ over $\betad$ distributions takes value at edge ($(0,0)$ point) as in Fig. \ref{fig_sensitivity}. But it's very smooth when move away from edge. Motivated by this, we apply smooth sensitivity in mechanism (v.s. global sensitivity) to improve accuracy.
\end{enumerate}
\end{column}
\begin{column}{.28\textwidth}
\begin{figure}[ht]
\centering
\includegraphics[width=0.9\textwidth]{poster_0.eps}
\caption{\footnotesize{Sensitivities of $\hellinger$ over $\betad$}}
\label{fig_sensitivity}
\end{figure}
% \vspace{.1cm}
\end{column}
\end{columns}

@@

  \item[-] $S(\dataobs)$, the smooth sensitivity:
  $
  S(\dataobs)=\max_{\dataobs' \in \{0,1\}^{n}}\big\{ LS(\dataobs') \cdot e^{-\gamma\cdot d(\dataobs,\dataobs')}\big\}
  $,
  where:
  \begin{itemize}
   \item $d$: Hamming distance between two data sets,

@@

  Fig. \ref{fig_sampling} gives the average Hellinger distance between the sampled results and true posterior, by sampling for $10k$ times under each data size configuration.
  In the baseline approach, it is enough to add noise with sensitivity $1$ in 2 dimensions and $2$ in higher dimensions since it's equivalent to histogram
  (Should explain better).
  giving us the red points in plots. Without the knowledge of equivalence, Laplace usually add noise with sensitivity scale to dimensions, giving us green points.
  Points in blue are given by the $\hexpmech$.

\begin{figure}[H]
\begin{center}
\centering
  \subfigure[\footnotesize{2 dimensions, data size $\in [100,500]$}]{
    \includegraphics[width=0.328\textwidth]{poster_1.eps}
    \label{subfig_sampling_2d}
  }
  \subfigure[\footnotesize{3 dimensions, data size $\in [100,500]$} ]{
    \includegraphics[width=0.297\textwidth]{poster_2.eps}
  \label{subfig_sampling_3d}
  } 
  \subfigure[\footnotesize{4 dimensions, data size $\in [100,600]$}]{
    \includegraphics[width=0.29\textwidth]{poster_3.eps}
    \label{subfig_sampling_4d}
  }
  \caption{Increasing data size}
\label{fig_sampling}
\end{center}
\end{figure}

Fig. \ref{fig_concrete_prob} gives us the concrete probabilities of outputting candidates with certain Hellinegr distance from the correct posterior in 2, 3 and 4 dimensions respectively.
\begin{figure}[H]
\begin{center}
\centering
  \subfigure[2 dimensions]{
    \includegraphics[width=0.31\textwidth]{poster_4.eps}
  \label{fig_concrete_prob_2d}
  }
  \subfigure[3 dimensions]{
    \includegraphics[width=0.31\textwidth]{poster_5.eps}
  \label{fig_concrete_prob_3d}
  } 
  \subfigure[4 dimensions]{
    \includegraphics[width=0.31\textwidth]{poster_6.eps}
  \label{fig_concrete_prob_4d}
  } 
\caption{The concrete outputting probabilities under different dimensions with data set of size $600$}
\label{fig_concrete_prob}
\end{center}
\end{figure}
\scriptsize{Two groups of experiments both with unit prior $\betad(1,1), \betad(1,1,1)$ and $\betad(1,1,1,1)$, balanced datasets and parameters $\epsilon = 1.0$ and $\delta = 10^{-8}$.}
\end{block}

@@

\begin{itemize}
\item The smoothed Hellinger distance based exponential mechanism outperforms the asymptotically the baseline 
  approach  when the latter uses a sensitivity proportional to dimensionality.
  (when can this happen?)
  % \begin{enumerate}
  %   \item  The accuracy that we are going to explore next, and in a more principled and formal way.

>>>>

\begin{block}{Bayesian inference ($\bysinfer$): Beta-Binomial model}
% The first subdivided column within the first main column
% \begin{columns} % Subdivide the first main column
% \begin{column}{.54\textwidth} % The first subdivided column within the first main column
%The prior $\betad(\alpha, \beta)$, with hyperparameters $\alpha,\beta\in\mathbb{R}^{+}$ is conjugate to the likelihood function.
\begin{itemize}
  \item[-] Prior on $\theta: \betad(\alpha, \beta), \alpha,\beta\in\mathbb{R}^{+}$, observed data set $\dataobs= (x_1,\dots x_n)\in\{0,1\}^{n}, n\in\mathbb{N}$.

@@

\begin{block}{Differentially Private Bayesian Inference and Motivations}
Releasing a differentially private posterior $\betad (\tilde\alpha,\tilde\beta)=(\alpha +  \widetilde{\Delta \alpha},\beta + n - \widetilde{\Delta \alpha})$.
\begin{columns} % Subdivide the first main column
\begin{column}{.69\textwidth}
\begin{enumerate}
  \item  Baseline approach samples noise from $\mathsf{Lap}(\Delta \alpha, \frac{1}{\epsilon})$ with mean $\Delta \alpha$ and scale $\frac{1}{\epsilon}$. But noise here is scaled to sensitivity $1$ over $\ell_1$ norm. Motivated by this, we calibrate the noise w.r.t sensitivity of the accuracy metric ($\hellinger$) (v.s. the $\ell_1$ norm in baseline approach).
  \item Global sensitivity of $\hellinger$ over $\betad$ distributions takes value at edge ($(0,0)$ point) as in Fig. \ref{fig_sensitivity}. But it's very smooth when move away from edge. Motivated by this, we apply smooth sensitivity in mechanism (v.s. global sensitivity) to improve accuracy.
\end{enumerate}
\end{column}
\begin{column}{.28\textwidth}
\begin{figure}[ht]
\centering
\includegraphics[width=0.9\textwidth]{poster_0.eps}
\caption{\footnotesize{Sensitivities of $\hellinger$ over $\betad$}}
\label{fig_sensitivity}
\end{figure}
% \vspace{.1cm}
\end{column}
\end{columns}

@@

  \item[-] $S(\dataobs)$, the smooth sensitivity\cite{nissim2007smooth}:
  $
  S(\dataobs)=\max_{\dataobs' \in \{0,1\}^{n}}\big\{ LS(\dataobs') \cdot e^{-\gamma\cdot d(\dataobs,\dataobs')}\big\}
  $,
  where:
  \begin{itemize}
   \item $d$: Hamming distance between two data sets,

@@

  Fig. \ref{fig_sampling} gives the average Hellinger distance between the sampled results and true posterior, by sampling for $10k$ times under each data size configuration.
  In the baseline approach (LapMech), it is enough to add noise with sensitivity $1$ in 2 dimensions and $2$ in higher dimensions since it's equivalent to histogram
  (Posteriors of adjacent data sets differ only in two dimensions),
  giving us the red points in plots. Without knowing equivalence, LapMech adds noise scaled to sensitivity proportional to dimensionality, giving us green points.
  Points in blue are given by the $\hexpmech$.

\begin{figure}[H]
\begin{center}
\centering
  \subfigure[\footnotesize{2 dimensions, data size $\in [100,500]$}]{
    \includegraphics[width=0.333\textwidth]{poster_1.eps}
    \label{subfig_sampling_2d}
  }
  \subfigure[\footnotesize{3 dimensions, data size $\in [100,500]$} ]{
    \includegraphics[width=0.302\textwidth]{poster_2.eps}
  \label{subfig_sampling_3d}
  } 
  \subfigure[\footnotesize{4 dimensions, data size $\in [100,600]$}]{
    \includegraphics[width=0.295\textwidth]{poster_3.eps}
    \label{subfig_sampling_4d}
  }
  \caption{Average accuracy by increasing data set size}
\label{fig_sampling}
\end{center}
\end{figure}

Fig. \ref{fig_concrete_prob} gives us the concrete probabilities of outputting candidates with certain Hellinegr distance from the correct posterior in 2, 3 and 4 dimensions respectively.
\begin{figure}[H]
\begin{center}
\centering
  \subfigure[2 dimensions]{
    \includegraphics[width=0.31\textwidth]{poster_4.eps}
  \label{fig_concrete_prob_2d}
  }
  \subfigure[3 dimensions]{
    \includegraphics[width=0.31\textwidth]{poster_5.eps}
  \label{fig_concrete_prob_3d}
  } 
  \subfigure[4 dimensions]{
    \includegraphics[width=0.31\textwidth]{poster_6.eps}
  \label{fig_concrete_prob_4d}
  } 
\caption{The concrete outputting probabilities under different dimensions with data set of size $600$}
\label{fig_concrete_prob}
\end{center}
\end{figure}
\footnotesize{Experiments above are with unit prior $\betad(1,1), \betad(1,1,1)$ and $\betad(1,1,1,1)$, balanced datasets, $\epsilon = 1.0$ and $\delta = 10^{-8}$.}
\end{block}

@@

\begin{itemize}
  \item The smoothed Hellinger distance based exponential mechanism outperforms asymptotically the baseline 
  approach  when the latter uses a sensitivity proportional to dimensionality.
  \item From experimental results, the outperformance happens when the data size is greater than $400$ .
  % \begin{enumerate}
  %   \item  The accuracy that we are going to explore next, and in a more principled and formal way.
